Structural controllability of ecological networks

### 2018-06-28 paper/manuscript.Rmd
Be explicit about delta and rho values in the main text figure
Close #50

```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the structural stability of the communities after a single focal species is removed. Mathematically, the structural stability of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances [@saavedra_nested_2016]. The structural stability of communities in which critical species have been removed (darker line) is considerable smaller than that of communities in which non-critical species have been removes. This indicates that critical species contribute more to the stable coexistence of their communities. To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one."}
drake::loadd(fig_structural_stability)
fig_structural_stability[[1]]
```

>>>>

```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the structural stability of the communities after a single focal species is removed. Mathematically, the structural stability of a network represents the size of the parameter space (i.e., growth rates, carrying capacities, etc.) under which all species can sustain positive abundances. The structural stability of communities in which critical species have been removed (darker line) is considerable smaller than that of communities in which non-critical species have been removes. This indicates that critical species contribute more to the stable coexistence of their communities. To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one. We assume intermediate values of the mutualistic trade-off and mean interspecific competition : $\\delta = 0.25$, $\\rho = 0.005$ [@saavedra_nested_2016]. However, the choice of parameters does not affect the results (Supporting Information \\@ref(S-structural-stability))"}
drake::loadd(fig_structural_stability)
fig_structural_stability[[1]]
```
